### 2013-02-20 paper/Analisis.tex
added line breaks
paragraph editting

\section*{Models}

We propose several models which include differents rotational
velocities and optical depths. We also take into account the dust
within the gas and two differents initial distributions of the
photons, central and homogeneous. At the end we study 48 models, those
are resumed in Table[1]\\ 
\\
\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|}
\hline
Velocity(km/s) & 50, 100, 200, 300\\
\hline
Optical Depth & $\tau = 10^{5},10^{6},10^{7}$\\
\hline
Photons Distributions & Central, Homogeneous\\
\hline
\end{tabular}
\caption{Models, If we take into account all these possibles
  combinations we get 24 models with dust and 24 without dust for a
  total of 48 models.} 
\end{center}
\end{table}

We later study this models taking into account the posititon of the
observer respect to the axis of rotation of the cloud.

\subsection*{Rotational Effect}

@@

In cartesian coordinates the rotational velocity around de the z-axys
is defined by:

\begin{subequations}
\begin{align}
    v_{x}=-\dfrac{y}{R}v \label{subeq1}\\
    v_{y}=\dfrac{x}{R}v \label{subeq2}
\end{align}
\end{subequations}

@@

>>>>

\section{Introduction}

@@

\section{Implementation of Rotation in CLARA}

We implement into CLARA the simplest model whereby a sphere rotates
with homogeneous angular velocity. We define a cartesian coordinate
system with its origin at the center of the sphere and the rotation
axis to be the $z$-axis, the velocity field in the gas can be written as

%In cartesian coordinates the rotational velocity around de the z-axys
%is defined by:

\begin{subequations}
\begin{align}
    v_{x}=-\dfrac{y}{R}V_{\max} \label{subeq1}\\
    v_{y}=\dfrac{x}{R}V_{\max} \label{subeq2}
\end{align}
\end{subequations}

@@

\section{Simulated Models in CLARA}
\label{sec:models}

%We propose several models which include differents rotational
%velocities and optical depths. We also take into account the dust
%within the gas and two differents initial distributions of the
%photons, central and homogeneous. At the end we study 48 models, those
%are resumed in Table[1]\\

We compute the emergent Lyman-$\alpha$ line for several models with
differents values for the maximal rotational velocity, hydrogend optical
depth, dust optical depth and initial distributions of the photons
with respect to the gas. There are in total 60 models with the input
parameters summarized in Table  \ref{table:models}.

% JF: digo que son 60 modelos porque estoy incluyendo los de velocidad cero.

%We later study this models taking into account the posititon of the
%observer respect to the axis of rotation of the cloud.

Additionaly in the postprocessing process we will take into account
different observer positions with respecto the cloud rotation
axis.

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline
Velocity (km s$^{-1}$) & $V_{\rm max}$&$0,\ 50,\ 100,\ 200,\ 300$\\
Hydrogen Optical Depth & $\tau_{H} $ & $10^{5},\ 10^{6},\ 10^{7}$\\
Dust Optical Depth & $\tau_{A}$ & XXX \\
Photons Distributions & & Central, Homogeneous\\
\hline
\end{tabular}
\caption{
Values for the varying input parameters in CLARA. Taking into account
all the possible combinations for these models
%odels, If we take into account all these possibles
% combinations we get 24 models with dust and 24 without dust for a
% total of 48 models 
} 
\label{table:models}
\end{center}
\end{table}
